Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of strategies in the Moran process for the Iterated Prisoner's

### 2018-01-11 main.tex
Mark minor modifications.

Interestingly none of these strategies is stochastic: this is explained by the
value of not provoking typically cooperative opponent strategies with
speculative defections. This includes opponents using the same strategy.  Acting
stochastically increases the chance of reducing the score of individuals of the
same type in a Moran process.  However it is possible to design a strategy with
a stochastic or error-correcting handshake that is an excellent resistor even in
noisy environments \cite{Lee2015}.

>>>>

Interestingly none of these strategies are stochastic: this is explained by the
value of not provoking typically cooperative opponent strategies with
speculative defections. This includes opponents using the same strategy.  Acting
stochastically increases the chance of reducing the score of individuals of the
same type in a Moran process.  However it is possible to design a strategy with
a stochastic or error-correcting handshake that is an excellent resistor even in
noisy environments \cite{Lee2015}.
